Supporting Information for "Imperfect slope measurements drive overestimation in geometric cone model of lake and reservoir depth"

### 2021-08-22 manuscript/si_template_2019.tex
title sync
sync title with ms word
add cfl affliation

\title{Supporting Information for "Imperfect slope measurements drive overestimation in standard cone model of lake depth"}
%
% e.g., \title{Supporting Information for "Terrestrial ring current:
% Origin, formation, and decay $\alpha\beta\Gamma\Delta$"}
%
%DOI: 10.1002/%insert paper number here%

@@

\authors{J. Stachelek\affil{1}, P. J. Hanly\affil{1}, and P. A. Soranno\affil{1}}

\affiliation{1}{Department of Fisheries and Wildlife, Michigan State University, 480
      Wilson Rd., East Lansing, MI 48824, USA}

>>>>

\title{Supporting Information for "Imperfect slope measurements drive overestimation in geometric cone model of lake and reservoir depth"}
%
% e.g., \title{Supporting Information for "Terrestrial ring current:
% Origin, formation, and decay $\alpha\beta\Gamma\Delta$"}
%
%DOI: 10.1002/%insert paper number here%

@@

\authors{J. Stachelek\affil{1,2}, P. J. Hanly\affil{1}, and P. A. Soranno\affil{1}}

\affiliation{1}{Department of Fisheries and Wildlife, Michigan State University, 480
      Wilson Rd., East Lansing, MI 48824, USA}
\affiliation{2}{Center for Limnology, University of Wisconsin – Madison, Madison, WI, USA}
